---
title: "1st Year Paper Stats for Iterated Number"
author: Sebastian Holt
output: html_notebook
---

```{r libraries, echo=FALSE}

library(lme4) # need for running lmer
library(tidyverse)
library(coda)
require(languageR)
library(lmerTest) #need this for lmer p values!!! Maybe it's not so important...
library(emmeans)
library(data.table)


```

```{r get_data, echo=FALSE}
# import the data that was output from internum_analysis.ipynb
# dat1 = read_csv("../results/csv/iterated_number_group_data_run1.csv")
# dat2 = read_csv("../results/csv/iterated_number_group_data_run2.csv")
# dat3 = read_csv("../results/csv/iterated_number_group_data_run3.csv")
# dat4 = read_csv("../results/csv/iterated_number_group_data_run4.csv")
# dat5 = read_csv("../results/csv/iterated_number_group_data_run5.csv")
dat6 = read_csv("../results/csv/iterated_number_group_data_run6.csv")
# dat = rbind(dat2, dat3, dat4, dat5, dat6)
# games = unique(dat$gameID)

dud_games = c(#"6769-3ee1e797-2c5b-4441-8d67-5ccd1c6b9a73",    #number
             "8369-76e6f73d-922a-4aca-b98a-8c96026aa48a",    #number
             "1372-60cdfd55-28bb-411c-b777-c51eaadee7a9",    #shape
             "2949-1e579088-8493-4c07-873c-7bd6d00685e3",    #shape
             "7197-6d1f3fda-040a-455c-aef0-279ba9aef053",    #shape
             "9237-4cc76e85-9955-4cef-b03c-5c68f46321ca",    #shape
             "1947-29382ba4-5747-456d-ba8b-276812fc1fb3")    #shape
bad_games <- dat6[ dat6$gameID %in% dud_games, ]
dat <- dat6[ ! dat6$gameID %in% dud_games, ]


dat_num = filter(dat,Game_Condition == 'number')
dat_aml = filter(dat,Game_Condition == 'shape')

```

Before beginning any analyses, just some summary statistics:
```{r accuracy_ttest}

# get accuracy data by game for all games
acc <- dat %>% group_by(Game_Condition, gameID) %>%
  count(outcome) %>% filter(outcome == TRUE)
  
# count up the accuracy by game in each condition, then store all in one dataframe
number_acc <- data.frame((acc %>% filter(Game_Condition == 'number'))$n)
shape_acc <- data.frame((acc %>% filter(Game_Condition == 'shape'))$n)
number_acc$cond <- 'number'
shape_acc$cond <- 'shape'
colnames(number_acc) <- c("N","cond")
colnames(shape_acc) <- c("N","cond")
all_accs <- rbind.data.frame(number_acc, shape_acc)

# now do the t-test comparing accuracy in each condition
acc_ttest <- t.test((acc %>% filter(Game_Condition == 'number'))$n,
                    (acc %>% filter(Game_Condition == 'shape'))$n)

# and plot the two distributions
ggplot(all_accs, aes(N, fill = cond)) + geom_density(alpha = 0.2)

```

Now look at average stroke count by condition and see if they differ:
```{r strokecount_ttest}
dat$numStrokes <- dat$numStrokes %>% as.numeric()

typeof(dat$numStrokes)
strokes <- dat %>% group_by(Game_Condition, gameID) %>% 
  summarise_at(vars(numStrokes), funs(mean(., na.rm=TRUE)))

aggregate(dat[, numStrokes], list(dat$Game_Condition), mean)
  
t.test((acc %>% filter(Game_Condition == 'number'))$n,
       (acc %>% filter(Game_Condition == 'shape'))$n)

```


First going to look for main effects of each important IV (number and animal) on each of our four DVs from the pre-reg
```{r num_main}
ik_num <- lm(data=dat, meanPixelIntensity ~ cardinality)
st_num <- lm(data=dat, numStrokes ~ cardinality) # significant of course
dr_num <- lm(data=dat, drawDuration ~ cardinality)
ac_num <- lm(data=dat, outcome ~ cardinality, family = 'binomial')
ik_num_stats <- c(round(anova(ik_num)[1,4],3), round(anova(ik_num)[1,5],3))
st_num_stats <- c(round(anova(st_num)[1,4],3), round(anova(st_num)[1,5],3))
dr_num_stats <- c(round(anova(dr_num)[1,4],3), round(anova(dr_num)[1,5],3))
ac_num_stats <- c(round(anova(ac_num)[1,4],3), round(anova(ac_num)[1,5],3))
```


```{r aml_main}
ik_aml <- lm(data=dat, meanPixelIntensity ~ category)
st_aml <- lm(data=dat, numStrokes ~ category) # significant of course
dr_aml <- lm(data=dat, drawDuration ~ category)
ac_aml <- lm(data=dat, outcome ~ category, family = 'binomial')
ik_aml_stats <- c(round(anova(ik_aml)[1,4],3), round(anova(ik_aml)[1,5],3))
st_aml_stats <- c(round(anova(st_aml)[1,4],3), round(anova(st_aml)[1,5],3))
dr_aml_stats <- c(round(anova(dr_aml)[1,4],3), round(anova(dr_aml)[1,5],3))
ac_aml_stats <- c(round(anova(ac_aml)[1,4],3), round(anova(ac_aml)[1,5],3))

# show it in a pretty way; figure out by and by, not sure what's the norm
# library(knitr)
# kable(c(as.character(ik_aml_stats),as.character(st_aml_stats)))
```
```{r interactions}
# looking to see what is the interaction of game condition with out main IVs not already explained by that IV
ik_CrdCnd <- lm(data=dat, meanPixelIntensity ~ cardinality*Game_Condition)
ik_CatCnd <- lm(data=dat, meanPixelIntensity ~ category*Game_Condition)
st_CrdCnd <- lm(data=dat, numStrokes ~ cardinality*Game_Condition)
st_CatCnd <- lm(data=dat, numStrokes ~ category*Game_Condition)
dr_CrdCnd <- lm(data=dat, drawDuration ~ cardinality*Game_Condition)
dr_CatCnd <- lm(data=dat, drawDuration ~ category*Game_Condition)
ac_CrdCnd <- lm(data=dat, outcome ~ cardinality*Game_Condition, family = 'binomial')
ac_CatCnd <- lm(data=dat, outcome ~ category*Game_Condition, family = 'binomial')
ik_CrdCnd_stats <- c(round(anova(ik_CrdCnd)[3,4],3), round(anova(ik_CrdCnd)[3,5],3))
ik_CatCnd_stats <- c(round(anova(ik_CatCnd)[3,4],3), round(anova(ik_CatCnd)[3,5],3))
st_CrdCnd_stats <- c(round(anova(st_CrdCnd)[3,4],3), round(anova(st_CrdCnd)[3,5],3))
st_CatCnd_stats <- c(round(anova(st_CatCnd)[3,4],3), round(anova(st_CatCnd)[3,5],3))
dr_CrdCnd_stats <- c(round(anova(dr_CrdCnd)[3,4],3), round(anova(dr_CrdCnd)[3,5],3))
dr_CatCnd_stats <- c(round(anova(dr_CatCnd)[3,4],3), round(anova(dr_CatCnd)[3,5],3))
ac_CrdCnd_stats <- c(round(anova(ac_CrdCnd)[3,4],3), round(anova(ac_CrdCnd)[3,5],3))
ac_CatCnd_stats <- c(round(anova(ac_CatCnd)[3,4],3), round(anova(ac_CatCnd)[3,5],3))

```


### predicting strokes from cardinality, category, and condition
```{r}
model.strokes <- lmer(data = dat,
                 numStrokes ~ cardinality * Game_Condition 
                 + (1 | gameID))
summary(model.strokes)

```


### several other maximal models
```{r maximal_models}
# for each DV (total ink, number of strokes, and draw duration) store the lmer
lmer_ink <- lmer(data = dat,
                 meanPixelIntensity ~ cardinality * category * Game_Condition * quarter
                 + (1 + cardinality * category | gameID))

lmer_str <- lmer(data = dat,
                 numStrokes ~ cardinality * category * Game_Condition * quarter
                 + (1 + cardinality * category | gameID))

lmer_dur <- lmer(data = dat,
                 drawDuration ~ cardinality * category * Game_Condition * quarter
                 + (1 + cardinality * category | gameID))

glmer_ac <- glmer(data=dat,
                  outcome ~ cardinality * category * Game_Condition * quarter
                  + (1 + cardinality * category | gameID),
                  family = 'binomial')
```
### These appear to not converge. So let's simplify the models
```{r reduced_models_comparisons}
# a set of models removing the category (animal) information from random effects
lmer_ink_car <- lmer(data = dat,
                 meanPixelIntensity ~ cardinality * category * Game_Condition * quarter
                 + (1 + cardinality | gameID))

lmer_str_car <- lmer(data = dat,
                 numStrokes ~ cardinality * category * Game_Condition * quarter
                 + (1 + cardinality | gameID))

lmer_dur_car <- lmer(data = dat,
                 drawDuration ~ cardinality * category * Game_Condition * quarter
                 + (1 + cardinality | gameID))

glmer_ac_car <- glmer(data=dat,
                  outcome ~ cardinality * category * Game_Condition * quarter
                  + (1 + cardinality | gameID),
                  family = 'binomial')

# a set of models removing the cardinality information from random effects
lmer_ink_cat <- lmer(data = dat,
                 meanPixelIntensity ~ cardinality * category * Game_Condition * quarter
                 + (1 + category | gameID))

lmer_str_cat <- lmer(data = dat,
                 numStrokes ~ cardinality * category * Game_Condition * quarter
                 + (1 + category | gameID))

lmer_dur_cat <- lmer(data = dat,
                 drawDuration ~ cardinality * category * Game_Condition * quarter
                 + (1 + category | gameID))

glmer_ac_cat <- glmer(data=dat,
                  outcome ~ cardinality * category * Game_Condition * quarter
                  + (1 + category | gameID),
                  family = 'binomial')


# a set of models removing the any slope in the random effects
lmer_ink_flat <- lmer(data = dat,
                 meanPixelIntensity ~ cardinality * category * Game_Condition * quarter
                 + (1 | gameID))

lmer_str_flat <- lmer(data = dat,
                 numStrokes ~ cardinality * category * Game_Condition * quarter
                 + (1 | gameID))

lmer_dur_flat <- lmer(data = dat,
                 drawDuration ~ cardinality * category * Game_Condition * quarter
                 + (1 | gameID))

glmer_ac_flat <- glmer(data=dat,
                  outcome ~ cardinality * category * Game_Condition * quarter
                  + (1 | gameID),
                  family = 'binomial')



```

```{r CLF_probabilities}
clf_dat = read_csv("../results/csv/CLF_targ_probs.csv")
clf_6 = clf_dat %>% filter(layer==6)
setnames(clf_6, "prob", "logprob")

test1 <- lm(data=clf_6, logprob ~ condition*clf) #  +  (1 | sketch_id)
summary(test1)

# https://vasishth-statistics.blogspot.com/2018/04/a-little-known-fact-paired-t-test-is.html
test2 <- lmer(data=clf_6, logprob ~ condition  +  (1 | sketch_id))
summary(test2)

ggplot(clf_6, aes(logprob, fill = condition)) + geom_density(alpha = 0.2)
```

